TODO: Nuno, please summarize these recent papers.  You can do this
only superficially on a first pass.  But it is important to do it
quickly to avoid surprises.  Some questions: Are they dealing with the
same problem as we are?  If no, is this problem really relevant?  If
yes, what is the advantage of our approach compared to theirs?

%%%%%%%
Which Configuration Option Should I Change?  ICSE'14

This paper tries to identify the configuration options that need to be changed/modified
so that a new version of the software behaves as an old version.

Our solution does not need an old version in order to do the analysis.

%%%%%%%
Automated Diagnosis of Software Configuration Errors.  ICSE'13

We are trying to address the same problem, but in a different way. They solve it by using
static analysis (thin slices) combined with dynamic analysis (of predicates). Instead, we
use a logic reasoning approach (we can identify multiple configuration errors, for instance).

As a major disadvantage of their approach is the fact that they need a rather complete pool
of correct executions in order for the approach to be able to identify what is erroneous.


%%%%%%%
Do Not Blame Users for Misconfigurations.  SOSP'13

This paper proposes SPEX, a technique that infers configuration contraints from source
code (statically) and uses the contraints to (1) expose (automatic testing) misconfigurations
and (2) detect certain types of error-prone configuration design and handling.

Our technique is light-weight when compared to this one and explores all sets of test
cases available and not only the configuration-oriented ones.


%%%%%%%
Failure Avoidance in Configurable Systems through Feature Locality. Assurances for Self-Adaptive Systems 2013

This technique determines common relationships between configurations, which can help to reactively
build recovery solutions and predict results of specific configurations. The hypothesis they have
worked well for gcc, but I am not so sure about it. 

It seems that this paper is orthogonal to what we are trying to achieve, and after we diagnose, it
can be used to recover from the set of features. It is interesting to think about that because it
paves the way to automatic diagnose and recovery.
